Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-07-25 arxivsub3/submission.tex
cleaning up

\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage{appendix}
\usepackage{authblk}
\usepackage{authblk}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage{xurl}

@@

\usepackage{setspace}
\onehalfspacing

@@

\begin{abstract}

Recent years have seen increasing efforts to forecast infectious disease burdens, with a primary goal being to help
public health workers make informed policy decisions. However, there has only been limited discussion of how
predominant forecast evaluation metrics might indicate the success of policies based in part on those forecasts. We
explore one possible tether between forecasts and policy: the allocation of limited medical resources so as to minimize
unmet need. We use probabilistic forecasts of disease burden in each of several regions to determine optimal resource
allocations, and then we score forecasts according to how much unmet need their associated allocations would have
allowed. We illustrate with forecasts of COVID-19 hospitalizations in the US, and we find that the forecast skill
ranking given by this allocation scoring rule can vary substantially from the ranking given by the weighted interval
score. We see this as evidence that the allocation scoring rule detects forecast value that is missed by traditional
accuracy measures and that the general strategy of designing scoring rules that are directly linked to policy
performance is a promising direction for epidemic forecast evaluation.

\end{abstract}

@@

\paragraph{Example 1} Suppose we have a forecast $F$ for need in two locations with $F_1 = \mathrm{Exp}(1 / \sigma_1)$
and $F_2 = \mathrm{Exp}(1 / \sigma_2)$, where $\sigma_1 = 1$ and $\sigma_2 = 4$. The means of these distributions are
given by the scale parameters $\sigma_i$. When the marginal forecasts are exponential distributions, it can be shown
that the optimal allocation divides the available resources among the locations proportionally to the scale parameters
$\sigma_i$ (see appendices \ref{sec:bayes-quantiles}). If $K = 5$ units of the resource are
available, the optimal allocation according to $F$ would be 1 and 4 resource units in locations 1 and 2, respectively. 
Increasing $K$ to $10$ changes this optimal allocation to 2 and 8. Figure~\ref{fig:exp_alloc_example} illustrates the 
situation.

@@

\paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} The Bayes act associated with the
forecast, $x^{F,K}$, is the allocation that minimizes the expected loss, that is, the solution of the \emph{allocation
problem} associated with $K$:
\begin{align}
  \underset{0 \leq x}{\mathrm{minimize}}\,\, \mathbb{E}_{F} [s_A(x, Y)] \text{ subject to }
  \, \sum_{i=1}^N x_i = K, \label{AP}
\end{align}
where $\mathbb{E}_{F} [s_A(x, Y)] = \sum_{i=1}^{N} L \cdot \mathbb{E}_{F_i}[\max(0, Y_i - x_i)]$ sums the expected loss
due to unmet need across all locations.

In appendix \ref{sec:bayes-quantiles} we show that the components of the Bayes act are quantiles 
$x_i^{F,K} = F_i^{-1}(\tau^{F,K})$ at a probability level $\tau^{F,K}$ that depends on the forecast $F$ and the resource
constraint $K$, but is shared across all locations. This probability level is the level at which the resource constraint
is satisfied: $\sum_{i=1}^N F_i^{-1}(\tau^{F,K}) = K$. This tells us that in order to allocate optimally (according to
$F$), we must divide resources among the locations so that there is an equal forecasted probability in every location
that the allocation is sufficient to meet resource need. This solution to the allocation problem is well-known in
inventory management and is often attributed to \cite{hadleywhitin1963}.

\paragraph{Step 3: Define the scoring rule.} We can now use the Bayes act to define a proper scoring rule for the
probabilistic forecast $F$. Consider first the ``raw'' score defined as
\begin{align}
  S_A^{\text{raw}}(F, y; K) = s_A(x^{F,K}, y) = \sum_{i=1}^N L \cdot \max(0, y_i - x_i^{F,K}).
\end{align}
This measures the total unmet need across all locations that results from using the Bayes allocation associated with the
forecast $F$ when the actual level of need in each location is observed to be $y_i$.

To make this a more easily interpreted measure of forecast performance, we will adjust the raw score by subtracting the
minimum loss achievable by an \emph{oracle} allocator which has precise foreknowledge of the outcomes $y_i$. When the
oracle has sufficient resources to meet the total need, i.e., when $\sum_{i=1}^{N}y_i \leq K$, the oracle's loss is zero
and allocation score coincides with the raw score. On the other hand, when the oracle cannot cover all need and incurs a
loss of $L \cdot \left(\sum_{i=1}^{N}y_i - K \right) > 0$, we adjust the raw score by this loss.
The oracle-adjusted score can therefore be written as
\begin{align}
  S_A(F, y; K)  &= S_A^{\text{raw}}(F, y; K) - L \cdot \max\left(0,\sum_{i=1}^{N}y_i - K\right) \\
  &= L\left\{\sum_{i=1}^N \max(0, y_i - x_i^{F,K}) -  \max\left(0,\sum_{i=1}^{N}y_i - K\right)\right\}.
\end{align}
The oracle adjustment aligns with a common theme in economic decision theory that \emph{opportunity loss} (often known
as \emph{regret} or (negative) \emph{relative utility}) is often a more important quantity than absolute loss (see e.g.,
\cite{DIECIDUE201788}).

@@

As described above, predictions were submitted to the Forecast Hub in the form of a set of 23 quantiles of the
predictive distribution. The WIS can be directly calculated from these quantiles. However, calculation of the AS
requires that the full cumulative distribution functions of the forecast distributions for each location are available.
For the purpose of this analysis, to calculate the allocation score we approximated the full cumulative distribution
functions based on the provided quantiles. On the interior of the provided quantiles we used a monotonic cubic spline to
interpolate the quantiles, and in the lower and upper tails we used normal distributions with parameters selected so as
to match the two lowest and two highest quantiles (see appendix \ref{sec:distfromq} for further details).
In appendix \ref{sec:propriety_of_parametric_approximation}, we show that if this evaluation procedure
had been specified prospectively, the resulting score would be proper, \textemdash but that a post hoc application of this
procedure is improper. We use the procedure here to illustrate the properties of the AS, and note that a collaborative
forecasting hub interested in using the AS for evaluation could circumvent propriety issues by communicating the
definition of the AS to forecasters and then collecting allocations at specified resource levels as part of forecast
submissions.

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Feb 23 19:04:47 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
\texttt{CU-select} & 669 & 133 & 774 & 326 \\ 
  \texttt{per-capita} & 865 & - & 1029 & 366 \\ 
  \texttt{COVIDhub-ensemble} & 873 & 159 & 1067 & 438 \\ 
  \texttt{USC-SI\_kJalpha} & 995 & 91 & 1216 & 1097 \\ 
  \texttt{JHUAPL-Gecko} & 1034 & 164 & 1141 & 418 \\ 
  \texttt{MUNI-ARIMA} & 1084 & 169 & 1248 & 440 \\ 
  \texttt{COVIDhub-trained\_ensemble} & 1089 & 169 & 1271 & 823 \\ 
  \texttt{COVIDhub-baseline} & 1175 & 170 & 1317 & 535 \\ 
  \texttt{JHUAPL-Bucky} & 1358 & 102 & 1566 & 1214 \\ 
  \texttt{JHUAPL-SLPHospEns} & 1540 & 129 & 1604 & 1102 \\ 
  \texttt{UVA-Ensemble} & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS), (see Section \ref{sec:ias_examp}). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Feb 23 19:04:51 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
model & MAS & taMWIS & taMWIS rank \\ 
  \hline
\texttt{COVIDhub-ensemble} & 389 & 70 & 2 \\ 
  \texttt{per-capita} & 464 & - & - \\ 
  \texttt{COVIDhub-trained\_ensemble} & 483 & 87 & 4 \\ 
  \texttt{CU-select} & 502 & 81 & 3 \\ 
  \texttt{JHUAPL-SLPHospEns} & 526 & 67 & 1 \\ 
  \texttt{COVIDhub-baseline} & 594 & 93 & 5 \\ 
  \texttt{JHUAPL-Bucky} & 643 & 112 & 7 \\ 
  \texttt{MUNI-ARIMA} & 707 & 116 & 8 \\ 
  \texttt{JHUAPL-Gecko} & 929 & 110 & 6 \\ 
  \texttt{USC-SI\_kJalpha} & 1473 & 155 & 9 \\ 
   \hline
\end{tabular}
\caption{Time averaged mean weighted interval scores (taMWIS) and mean allocation scores (MAS) by model across 13 weeks. These results show the average performance across time for the nine models that submitted forecasts for every week from 2021-11-29 through 2022-02-21, as well
  as for a per-capita allocation. MWIS is not defined for the \texttt{per-capita} allocation which does not use forecasts.} 
\label{tab:multi-week-performance-summary}
\end{table}

@@

In practice, epidemiological forecasts are often directed at a diverse set of end-users. It may be easy for some of
these users to summarize the consequences of how they use a forecast with a numerical loss function, but for others,
such as officials deciding how best to update public ``situational awareness'' of an outbreak, this may be essentially
impossible. Even those forecast uses that are easily framed as expected loss minimization may differ enough that no
single score would be appropriate for all users. Ideally, targeted forecasting tools could be developed through close
collaboration between modelers and public health officials. However, this may only be possible in settings with
sufficient staffing on both an analytics and a public health team. Increasingly, collaborative modeling hubs are being
used to generate ``one-size-fits-all'' forecasts for many locations at once. But it could still be beneficial in these
settings to expand the set of scoring methods used by the hub to include scores, such as the AS, which are based on
specific public health decision problems.  This could help end users better understand the value of available forecasts
as inputs to their particular decision making contexts. (We note that issues of propriety are raised when forecasts are
evaluated with scoring rules for which they were not elicited or via parameters imputed by a hub after submission, both
of which are done in our application example.  We consider these issues briefly in appendices
\ref{sec:distfromq} and \ref{sec:propriety_of_parametric_approximation}.)

There are several important limitations to the current work. The allocation score we developed here does not directly
account for important considerations such as fairness or equity of allocations, or more broadly, individual and group
preference relations that are difficult or even impossible to encode into a loss or utility function.  Ambiguity aversion
(in the sense of \cite{ellsberg1961risk}), for example, seems especially relevant to the use of forecasts in outbreak
response, where there can be immense social and political pressure on public health officials to maintain a transparent
base of evidence for their policy choices and recommendations. The proposed framework also does not attempt to capture
the broader context of decision making. For example, in practice it may be possible to increase the resource constraint
$K$ by shifting funding from other disease mitigation measures. Finally, we emphasize that we opted at this stage of
development to explicitly rule out situations where a ``successful''
epidemiological forecast could lead to policy decisions that change the distribution of the predicted outcome $Y$. Our
framework would need considerable enhancements before being applicable to forecast evaluation beyond horizons for which
causal feedback can be neglected.

An opportunity for further investigation is to more carefully evaluate whether forecasts add value to 
``standard operating procedures'' already in place for making public health decisions. In the context of allocations,
such a procedure might extrapolate need from current observed need and population levels (similarly to the two benchmark
approaches presented above), with adjustments based on other political or real-world considerations. For example, in
many settings public health stakeholders will make decisions after synthesizing information from a variety of
quantitative and qualitative sources coupled with expert judgment. The allocation score presented in this work does not
directly measure whether a given forecast adds useful information to such an existing decision-making process. While the
scoring procedures as presented do not directly address this question, they could be modified (say, by comparison to a
`baseline' model or expert-elicited allocations in the absence of forecast data) to quantify the benefit of using a
forecast to inform a specific decision.

@@

\end{thebibliography}

\end{document}

>>>>

\usepackage[letterpaper,top=2cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage{appendix}
\usepackage{authblk}
\usepackage{authblk}
\usepackage{amsmath, amsfonts, amssymb}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{amsthm}
\usepackage{bm}
\usepackage{cases}
\usepackage{caption}
\usepackage{xr-hyper}
\usepackage{hyperref}
\usepackage{xurl}

@@

\usepackage{setspace}
\singlespacing

@@

\begin{abstract}
Recent years have seen increasing efforts to forecast infectious disease burdens, with a primary goal being to help
public health workers make informed policy decisions. However, there has only been limited discussion of how
predominant forecast evaluation metrics might indicate the success of policies based in part on those forecasts. We
explore one possible tether between forecasts and policy: the allocation of limited medical resources so as to minimize
unmet need. We use probabilistic forecasts of disease burden in each of several regions to determine optimal resource
allocations, and then we score forecasts according to how much unmet need their associated allocations would have
allowed. We illustrate with forecasts of COVID-19 hospitalizations in the US, and we find that the forecast skill
ranking given by this allocation scoring rule can vary substantially from the ranking given by the weighted interval
score. We see this as evidence that the allocation scoring rule detects forecast value that is missed by traditional
accuracy measures and that the general strategy of designing scoring rules that are directly linked to policy
performance is a promising direction for epidemic forecast evaluation.
\end{abstract}

\noindent \textbf{Keywords:} public health, forecast evaluation, proper scoring rules, resource allocation, epidemiology

@@

\paragraph{Example 1} Suppose we have a forecast $F$ for need in two locations such that $F_1$ and $F_2$ have exponential marginal distribution with scale parameters $\sigma_1 = 1$ and $\sigma_2 = 4$. The means of these distributions are
given by the scale parameters $\sigma_i$. When the marginal forecasts are exponential distributions, it can be shown
that the optimal allocation divides the available resources among the locations proportionally to the scale parameters
$\sigma_i$ (see appendix \ref{sec:a:bayes-quantiles}). If $K = 5$ units of the resource are
available, the optimal allocation according to $F$ would be 1 and 4 resource units in locations 1 and 2, respectively. 
Increasing $K$ to $10$ changes this optimal allocation to 2 and 8. Figure~\ref{fig:exp_alloc_example} illustrates the 
situation.

@@

\paragraph{Step 2: Given a probabilistic forecast $F$, identify the Bayes act.} The Bayes act associated with the
forecast, $x^{F,K}$, is the allocation that minimizes the expected loss, that is, the solution of the \emph{allocation
problem} associated with $K$:
\begin{align}
  \underset{0 \leq x}{\mathrm{minimize}}\,\, \mathbb{E}_{F} [s_A(x, Y)] \text{ subject to }
  \, \sum_{i=1}^N x_i = K, \label{eqn:AP}
\end{align}
where $\mathbb{E}_{F} [s_A(x, Y)] = \sum_{i=1}^{N} L \cdot \mathbb{E}_{F_i}[\max(0, Y_i - x_i)]$ sums the expected loss
due to unmet need across all locations.

In appendix \ref{sec:a:bayes-quantiles} we show that the components of the Bayes act are quantiles 
$x_i^{F,K} = F_i^{-1}(\tau^{F,K})$ at a probability level $\tau^{F,K}$ that depends on the forecast $F$ and the resource
constraint $K$, but is shared across all locations. This probability level is the level at which the resource constraint
is satisfied: $\sum_{i=1}^N F_i^{-1}(\tau^{F,K}) = K$. This tells us that in order to allocate optimally (according to
$F$), we must divide resources among the locations so that there is an equal forecasted probability in every location
that the allocation is sufficient to meet resource need. This solution to the allocation problem is well-known in
inventory management and is often attributed to \cite{hadleywhitin1963}.

\paragraph{Step 3: Define the scoring rule.} We can now use the Bayes act to define a proper scoring rule for the
probabilistic forecast $F$. Consider first the raw score defined as
\begin{align}
  S_A^{\text{raw}}(F, y; K) = s_A(x^{F,K}, y) = \sum_{i=1}^N L \cdot \max(0, y_i - x_i^{F,K}).
\end{align}
This measures the total unmet need across all locations that results from using the Bayes allocation associated with the
forecast $F$ when the actual level of need in each location is observed to be $y_i$.

To make this a more easily interpreted measure of forecast performance, we will adjust the raw score by subtracting the
minimum loss achievable by an \emph{oracle} allocator which has precise foreknowledge of the outcomes $y_i$. When the
oracle has sufficient resources to meet the total need, i.e., when $\sum_{i=1}^{N}y_i \leq K$, the oracle's loss is zero
and allocation score coincides with the raw score. On the other hand, when the oracle cannot cover all need and incurs a
loss of $L \cdot \left(\sum_{i=1}^{N}y_i - K \right) > 0$, we adjust the raw score by this loss.
The oracle-adjusted score can therefore be written as
\begin{align}
  S_A(F, y; K)  &= S_A^{\text{raw}}(F, y; K) - L \cdot \max\left(0,\sum_{i=1}^{N}y_i - K\right) \\
  &= L\left\{\sum_{i=1}^N \max(0, y_i - x_i^{F,K}) -  \max\left(0,\sum_{i=1}^{N}y_i - K\right)\right\}.
\end{align}
The oracle adjustment aligns with a common theme in economic decision theory that opportunity loss (often known
as regret or (negative) relative utility) is often a more important quantity than absolute loss (see e.g.,
\cite{DIECIDUE201788}).

@@

As described above, predictions were submitted to the Forecast Hub in the form of a set of 23 quantiles of the
predictive distribution. The WIS can be directly calculated from these quantiles. However, our numerical method for calculating 
the AS (outlined in appendix \ref{sec:a:numeric})
requires a full cumulative distribution function (CDF) for the forecast in each location.
For the purpose of this analysis, we imputed CDFs based on the provided quantiles following a procedure detailed in 
appendix \ref{sec:a:distfromq}. Briefly, this involves interpolating the provided quantiles between the lowest (.01) and highest 
(.99) probability levels using monotonic cubic splines, and then extending outside these levels with normal distribution tails
parametrized to match the two lowest and two highest quantiles. We show in appendix \ref{sec:a:propriety_of_parametric_approximation}
that if this evaluation procedure
had been specified prospectively, the resulting score would be proper, but that a post hoc application of this
procedure is improper. We use the procedure here to illustrate the properties of the AS, and note that a collaborative
forecasting hub interested in using the AS for evaluation could circumvent propriety issues by communicating the
definition of the AS to forecasters and then collecting allocations at specified resource levels as part of forecast
submissions.

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Mar  1 16:18:50 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
Model & AS & MWIS & IAS centered at 15k & IAS uniform \\ 
  \hline
\texttt{CU-select} & 669 & 133 & 774 & 326 \\ 
  \texttt{per-capita} & 865 & - & 1029 & 366 \\ 
  \texttt{COVIDhub-ensemble} & 873 & 159 & 1067 & 438 \\ 
  \texttt{USC-SI\_kJalpha} & 995 & 91 & 1216 & 1097 \\ 
  \texttt{JHUAPL-Gecko} & 1034 & 164 & 1141 & 418 \\ 
  \texttt{MUNI-ARIMA} & 1084 & 169 & 1248 & 440 \\ 
  \texttt{COVIDhub-trained\_ensemble} & 1089 & 169 & 1271 & 823 \\ 
  \texttt{COVIDhub-baseline} & 1175 & 170 & 1317 & 535 \\ 
  \texttt{JHUAPL-Bucky} & 1358 & 102 & 1566 & 1214 \\ 
  \texttt{JHUAPL-SLPHospEns} & 1540 & 129 & 1604 & 1102 \\ 
  \texttt{UVA-Ensemble} & 2469 & 213 & 2635 & 2494 \\ 
   \hline
\end{tabular}
\caption{For one illustrative week, a comparison of allocation scores (AS), mean weighted interval scores (MWIS), and two varieties of Integrated Allocation Scores (IAS), (see Section \ref{sec:ias_examp}). All metrics are shown for 10 models that made forecasts of hospital admissions for 2022-01-03. Results are sorted by AS. For all metrics, lower scores indicate better accuracy.} 
\label{tab:multi-k-scores}
\end{table}

@@

% latex table generated in R 4.3.1 by xtable 1.8-4 package
% Fri Mar  1 16:18:55 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrrr}
  \hline
model & MAS & taMWIS & taMWIS rank \\ 
  \hline
\texttt{COVIDhub-ensemble} & 389 & 70 & 2 \\ 
  \texttt{per-capita} & 464 & - & - \\ 
  \texttt{COVIDhub-trained\_ensemble} & 483 & 87 & 4 \\ 
  \texttt{CU-select} & 502 & 81 & 3 \\ 
  \texttt{JHUAPL-SLPHospEns} & 526 & 67 & 1 \\ 
  \texttt{COVIDhub-baseline} & 594 & 93 & 5 \\ 
  \texttt{JHUAPL-Bucky} & 643 & 112 & 7 \\ 
  \texttt{MUNI-ARIMA} & 707 & 116 & 8 \\ 
  \texttt{JHUAPL-Gecko} & 929 & 110 & 6 \\ 
  \texttt{USC-SI\_kJalpha} & 1473 & 155 & 9 \\ 
   \hline
\end{tabular}
\caption{Time averaged mean weighted interval scores (taMWIS) and mean allocation scores (MAS) by model across 13 weeks. These results show the average performance across time for the nine models that submitted forecasts for every week from 2021-11-29 through 2022-02-21, as well
  as for a per-capita allocation. MWIS is not defined for the \texttt{per-capita} allocation which does not use forecasts.} 
\label{tab:multi-week-performance-summary}
\end{table}

@@

In practice, epidemiological forecasts are often directed at a diverse set of end-users. It may be easy for some of
these users to summarize the consequences of how they use a forecast with a numerical loss function, but for others,
such as officials deciding how best to update public ``situational awareness'' of an outbreak, this may be essentially
impossible. Even those forecast uses that are easily framed as expected loss minimization may differ enough that no
single score would be appropriate for all users. Ideally, targeted forecasting tools could be developed through close
collaboration between modelers and public health officials. However, this may only be possible in settings with
sufficient staffing on both an analytics and a public health team. Increasingly, collaborative modeling hubs are being
used to generate ``one-size-fits-all'' forecasts for many locations at once. But it could still be beneficial in these
settings to expand the set of scoring methods used by the hub to include scores, such as the AS, which are based on
specific public health decision problems.  This could help end users better understand the value of available forecasts
as inputs to their particular decision making contexts. (We note that issues of propriety are raised when forecasts are
evaluated with scoring rules for which they were not elicited or via parameters imputed by a hub after submission, both
of which are done in our application example.  We consider these issues briefly in appendices
\ref{sec:a:distfromq} and \ref{sec:a:propriety_of_parametric_approximation}.)

There are several important limitations to the current work. The allocation score we developed here does not directly
account for important considerations such as fairness or equity of allocations, or more broadly, individual and group
preference relations that are difficult or even impossible to encode into a loss or utility function.  Ambiguity aversion
(in the sense of \cite{ellsberg1961risk}), for example, seems especially relevant to the use of forecasts in outbreak
response, where there can be immense social and political pressure on public health officials to maintain a transparent
base of evidence for their policy choices and recommendations. The proposed framework also does not attempt to capture
the broader context of decision making. For example, in practice it may be possible to increase the resource constraint
$K$ by shifting funding from other disease mitigation measures. Finally, we emphasize that we opted at this stage of
development to explicitly rule out situations where a successful
epidemiological forecast could lead to policy decisions that change the distribution of the predicted outcome $Y$. Our
framework would need considerable enhancements before being applicable to forecast evaluation beyond horizons for which
causal feedback can be neglected.

An opportunity for further investigation is to more carefully evaluate whether forecasts add value to 
standard  procedures already in place for making public health decisions. In the context of allocations,
such a procedure might extrapolate need from current observed need and population levels (similarly to the two benchmark
approaches presented above), with adjustments based on other political or real-world considerations. For example, in
many settings public health stakeholders will make decisions after synthesizing information from a variety of
quantitative and qualitative sources coupled with expert judgment. The allocation score presented in this work does not
directly measure whether a given forecast adds useful information to such an existing decision-making process. While the
scoring procedures as presented do not directly address this question, they could be modified (say, by comparison to a
baseline model or expert-elicited allocations in the absence of forecast data) to quantify the benefit of using a
forecast to inform a specific decision.

@@

\end{thebibliography}
\end{document}
